---
title: "fig_tbl"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal

This markdown produces the figures and tables used in ``locally anisotropic covariance functions on the sphere'', starting from Figure 4.

```{r libs and source, eval = T, echo = F, include = F}
rm(list = ls())
devtools::install_github("https://github.com/katzfuss-group/GPvecchia", 
                         ref = "JJ")
source("func.R")
```

## Figure 4

```{r fig 4, eval = F}
fig4 <- function(){
    set.seed(1)
    alpha <- c(-0.7, 0.35, 0.44)  
    beta <- c(-1.2, 0.25, 0.44)  
    kappa <- 0
    range <- - 2 / log(0.05)
    nu <- 0.5
    nuggets = 0.05^2
    nsrt <- 50
    grd.obj <- grd_gen(nsrt)
    z.all <- z_gen(alpha, beta, grd.obj$grd.all, kappa, nu, range, nuggets)
    sphere_plot(z.all, rep(T, length(z.all)), grd.obj$lon, grd.obj$lat,
                draw.palette = T, fn = "example_alldata.pdf")
}
fig4()
```

## Figure 5

Setting the `range` parameter to `0.1`, in the isotropic case, we have on average $29$ responses that are correlated with each response by more than $5\%$.
```{r fig 5 6 7 tbl 1, eval = F, echo=FALSE}
sim_study <- function(type = c("iso", "axially", "nonsta"), plot.flag = F, 
                      seed = 1){
    set.seed(seed)
    type = type[1]
    if(type == "iso"){
        alpha <- c(-0.5, 0.0, 0.0)  
        beta <- c(-0.5, 0.0, 0.0)  
        kappa <- 0
    }else if(type == "axially"){
        alpha <- c(-0.5, 0.0, 1.44)  
        beta <- c(-3.2, 0.0, 1.44)  
        kappa <- 0
    }else if(type == "nonsta"){
        alpha <- c(-0.5, -1.2, 1.44)  
        beta <- c(-3.2, -0.3, 1.44)  
        kappa <- 0.8
    }else{
        stop("Unsupported covariance type\n")
    }
    range <- 0.1
    nu <- 0.5
    nuggets = 0.05^2
    nsrt <- 50
    ns <- nsrt^2
    grd.obj <- grd_gen(nsrt)
    z.all <- z_gen(alpha, beta, grd.obj$grd.all, kappa, nu, range, nuggets)
    if(plot.flag)
        sphere_plot(z.all, rep(T, length(z.all)), grd.obj$lon, grd.obj$lat, 
                    draw.palette = T, 
                    fn = paste0("results/", type, "-true.pdf"), zlim = c(-3, 3))
    sim_func(ns = ns, grd.obj = grd.obj, z.all = z.all, nu = nu, 
             range = range, nuggets = nuggets, type = type, seed = seed)
}
sim_study("iso", seed = 1)
```

```{r plot sim data rslt, eval = F}
for(fn in list.files(pattern = "(rect|rand).*RData")){
    load(fn)
    sphere_plot(z.all = input$z.all, mask = input$mask, lon = input$lon, 
                lat = input$lat, draw.palette = T, 
                fn = input$fn, fig.width = 11.11, fig.height = 8.33, 
                zlim = c(-3, 3))
}
```

## Real Data Application Temperature

```{r real data temperature, eval = F}
real_app <- function(test.flag = F, plot.flag = F)
{
    set.seed(1)
    data <- nc_open("tas_Amon_GFDL-CM3_rcp26_r1i1p1_200601-201012.nc")
    lon <- as.numeric(ncvar_get(data, "lon") / 180 * pi - pi)
    lat <- as.numeric(ncvar_get(data, "lat") / 180 * pi)
    time <- as.numeric(ncvar_get(data, "time"))
    tas <- ncvar_get(data, "tas")
    idx.time <- 48
    idx.time.mean <- seq(from = 12, to = length(time), by = 12)
    z.all <- as.vector(tas[, , idx.time])
    if(test.flag){
        lon.idx <- round(seq(from = 1, to = length(lon), length.out = 72))
        lat.idx <- round(seq(from = 1, to = length(lat), length.out = 45))
        lon <- lon[lon.idx]
        lat <- lat[lat.idx]
        z.all <- as.vector(tas[lon.idx, lat.idx, idx.time])
    }
    grd.all <- as.matrix(expand.grid(lon, lat))
    grd.obj <- list(lon = lon, lat = lat, grd.all = grd.all)
    ns <- length(z.all)
    z.mean <- tas[, , idx.time.mean[1]]
    for(i in 2 : length(idx.time.mean))
        z.mean = z.mean + tas[, , idx.time.mean[i]]
    z.mean = z.mean / length(idx.time.mean)
    z.all <- (z.all - as.vector(z.mean))
    z.all <- z.all / sd(z.all)
    if(plot.flag)
        sphere_plot(z.all, rep(T, length(z.all)), lon, lat, fig.width = 13.44, 
                    fig.height = 8.73, draw.palette = T, fn = "Dec2019Temp.pdf")
    sim_func(ns = ns, grd.obj = grd.obj, z.all = z.all, nu = 2.5, 
             range = 0.1, nuggets = 0.05^2, type = "real", plot.flag = plot.flag)
}
real_app(test.flag = F, plot.flag = T)
```

## Real Data Application Precipitation

```{r real data precipitation, eval = F}
real_app <- function(plot.flag = F)
{
    set.seed(1)
    load(file='data/prec_all.RData') # lon,lat,prec
    x=log(prec+1e-10)
    x=scale(t(x)) # standardize
    lon <- unique(as.numeric(lon / 180 * pi - pi))
    lat <- unique(as.numeric(lat / 180 * pi))
    z.all <- matrix(x[1, ], 288, 192, byrow = F)
    # down-scaling
    idx.lon <- seq(from = 1, to = length(lon), by = 2)
    idx.lat <- seq(from = 1, to = length(lat), by = 2)
    lon <- lon[idx.lon]
    lat <- lat[idx.lat]
    z.all <- z.all[idx.lon, idx.lat]
    # Fit GP
    grd.all <- as.matrix(expand.grid(lon, lat))
    grd.obj <- list(lon = lon, lat = lat, grd.all = grd.all)
    ns <- length(z.all)
    if(plot.flag)
        sphere_plot(z.all, rep(T, length(z.all)), lon, lat, fig.width = 13.44, 
                    fig.height = 8.73, draw.palette = T, fn = "Prcp.pdf")
    sim_func(ns = ns, grd.obj = grd.obj, z.all = z.all, nu = 2.5, 
             range = 0.1, nuggets = 0.05^2, type = "real", plot.flag = plot.flag)
}
real_app(plot.flag = T)
```

## Export data into csv

This part is written for the transport map experiment.
```{r export csv, eval = F}
export_temp <- function(){
    data <- nc_open("tas_Amon_GFDL-CM3_rcp26_r1i1p1_200601-201012.nc")
    lon <- as.numeric(ncvar_get(data, "lon") / 180 * pi - pi)
    lat <- as.numeric(ncvar_get(data, "lat") / 180 * pi)
    time <- as.numeric(ncvar_get(data, "time"))
    tas <- ncvar_get(data, "tas")
    idx.time.mean <- seq(from = 12, to = length(time), by = 12)
    grd.all <- as.matrix(expand.grid(lon, lat))
    ## order & condition based on 3D coordinates
    l=grd.all[, 1]
    L=grd.all[, 2]
    locs=cbind(cos(L)*cos(l), cos(L)*sin(l), sin(L))
    z.mean <- tas[, , idx.time.mean[1]]
    for(i in 2 : length(idx.time.mean))
        z.mean <- z.mean + tas[, , idx.time.mean[i]]
    z.mean <- z.mean / length(idx.time.mean)
    rslt <- matrix(NA, 3 + length(idx.time.mean), nrow(grd.all))
    rslt[1 : 3, ] <- t(locs)
    for(i in 1 : length(idx.time.mean)){
        rslt[i + 3, ] <- as.vector(tas[, , idx.time.mean[i]] - 
                                       z.mean)
    }
    write.table(rslt, file = paste0("temp", ".csv"), sep = ',', col.names = F,
                row.names = F)
}
export_temp()
```

## Plot Figures with RData

```{r plot from RData, eval = F}
RDNames <- grep("*.RData", dir("./results/"), value = T)
for(fn in RDNames){
    fn <- paste0("results/", fn)
    load(fn)
    input$draw.palette <- T
    if(length(grep("results/", input$fn)) == 0)
        input$fn <- paste0("results/", input$fn)
    do.call(sphere_plot, input)
}

```

## Combina results from simulation replicates

```{r results from sim reps, eval = F}
nrep = 5
tbl.iso <- read.table("results/tbl_iso_1.out", sep = '&', 
                          comment.char = '\\')
tbl.axially <- read.table("results/tbl_axially_1.out", sep = '&', 
                          comment.char = '\\')
tbl.nonsta <- read.table("results/tbl_nonsta_1.out", sep = '&', 
                          comment.char = '\\')
for(i in 2 : nrep){
    tbl.iso <- tbl.iso + read.table(
        paste0("results/tbl_iso_", i, ".out"), sep = '&', 
        comment.char = '\\')
    tbl.axially <- tbl.axially + read.table(
        paste0("results/tbl_axially_", i, ".out"), sep = '&', 
        comment.char = '\\')
    tbl.nonsta <- tbl.nonsta + read.table(
        paste0("results/tbl_nonsta_", i, ".out"), sep = '&', 
        comment.char = '\\')
}
tbl.iso <- tbl.iso / nrep
tbl.axially <- tbl.axially / nrep
tbl.nonsta <- tbl.nonsta / nrep
for (type in c("iso", "axially", "nonsta"))
    write.table(format(get(paste0("tbl.", type)), digits = 4), 
                paste0("results/tbl_", type, ".out"), 
                sep = " & ", eol = "\\\\\n", quote = F)    

```











